Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-11-18 paper/ifo-complexAudio.tex
updating figures and slight edit of abstract

\begin{figure*}
	\begin{center}
    %% trim order is <left> <lower> <right> <upper>
    % height=0.5\textheight,trim={1cm 4.5cm 0.4cm 3.5cm},clip
	\includegraphics[height=0.85\textheight]{figures/notch_and_wiener_superplot_v2.pdf}
	\end{center}
	\caption{\label{fig:BackgroundNotchWienerCombined}
	Time series (left column) and frequency spectrum (right column) results for the background subtraction, notch, and Wiener filters.
	The first and second rows show the original speech recording and raw output from the optical microphone respectively. 
    The third row shows a background noise recording from the optical microphone when no audio signal is played. 
    The fourth row shows the result of subtracting the background noise spectrum in the third row from the recording in the second row. 
	%The second row shows the raw output from the optical microphone.
	%The third row shows the naive technique of subtracting off the noise spectrum from the recorded spectrum.
	The fifth, sixth, and seventh rows show the results of applying the notch filter, the Wiener filter, and both combined, respectively.
	}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=0.8\textwidth]{figures/combined_timeseries_melatos.pdf}
	\caption{Time series of an adult male voice (saying ``A cathode ...'') showing the source (top panel), the optical microphone recording (middle panel), and the recording after filtering with the logMMSE estimator (bottom panel). One second of the one minute recording is shown. The rise at the start of the bottom panel is expected when filtering a signal of finite duration.}
	\label{fig:logMMSE_timeseries}
\end{figure*}

>>>>

\begin{figure*}
	\begin{center}
    %% trim order is <left> <lower> <right> <upper>
    % height=0.5\textheight,trim={1cm 4.5cm 0.4cm 3.5cm},clip
	\includegraphics[width=.85\textwidth, trim={1cm 3cm 1cm 1cm}]{figures/notch_and_wiener_superplot_v2.pdf}
	\end{center}
	\caption{\label{fig:BackgroundNotchWienerCombined}
	Time series (left column) and frequency spectrum (right column) results for the background subtraction, notch, and Wiener filters.
	The first and second rows show the original speech recording and raw output from the optical microphone respectively. 
    The third row shows a background noise recording from the optical microphone when no audio signal is played. 
    The fourth row shows the result of subtracting the background noise spectrum in the third row from the recording in the second row. 
	%The second row shows the raw output from the optical microphone.
	%The third row shows the naive technique of subtracting off the noise spectrum from the recorded spectrum.
	The fifth, sixth, and seventh rows show the results of applying the notch filter, the Wiener filter, and both combined, respectively.
	}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=0.8\textwidth]{figures/combined_timeseries_melatos_shift_source.pdf}
	\caption{Time series of an adult male voice (saying ``A cathode ...'') showing the source (top panel), the optical microphone recording (middle panel), and the recording after filtering with the logMMSE estimator (bottom panel). One second of the one minute recording is shown. The rise at the start of the bottom panel is expected when filtering a signal of finite duration.}
	\label{fig:logMMSE_timeseries}
\end{figure*}
